\large{\bf Looking forwards and backwards through locally regulated populations }

### 2022-09-01 forwards-and-backwards.tex
.

The model we work with is a fairly general model
of individuals living in continuous space.
We start with a population of
$\bigO(N)$ individuals per unit area distributed in $\mathbb{R}^d$.
For applications, $d=1$ or $d=2$, but our results apply more generally.
The population will be distributed over a bounded region,
so the total number of individuals will also be $\bigO(N)$.
The population changes in continuous time, and
we describe the state of the population at time $t$ with a counting measure $X(t)$,
which assigns one unit of mass to the location of each individual.

@@

\begin{definition}[Martingale Problem Characterisation]
    \label{defn:mgale_construction},
For each value of $N$ and $\theta = \theta(N)$,
we define $(\eta^N_t)_{t \geq 0}$ to be the solution to the Martingale Problem,
with initial condition $\eta^N_0 \in \measures$,
such that for all smooth functions $f \in C^{\infty}_{0}(\mathbb{R}^d)$,
writing $\langle f, \eta \rangle = \int_{\IR^d} f(x) \eta(dx)$
and $q_\theta(x, dy)$ as the Gaussian kernel
with mean $x + \meanq(x)/\theta$ and covariance $\covq(x) / \theta$,
\begin{equation}
    \label{eqn:eta_martingale}
\begin{aligned}
M^N_t(f)
&:=  \langle f, \eta^N_t \rangle
        -\langle f, \eta^N_0 \rangle
 \\ &\qquad {}
 -  \int_{0}^{t}\bigg\{
        \int\left( \int \theta
             \left(
                f(z)r(z, \eta^N_{s})
                - f(x)r(x, \eta^N_{s})
            \right)
        q_\theta(x,dz) \right)
\\ & \qquad \qquad \qquad \qquad {}
        \times \gamma(x, \eta^N_{s}) \eta^N_{s}(dx)
\\ & \qquad \qquad {}
    + \int f(x) F(x, \eta^N_{s}) \eta^N_{s}(dx)
    \bigg\} ds
\end{aligned}    
\end{equation}
is a martingale with quadratic variation
    \begin{equation} \label{eqn:prelimit_martingale_variation}
\begin{aligned} \relax
[ M^N_t(f)] =& 
\frac{\theta}{N} \int_{0}^{t}\bigg\{
    \langle \gamma(x, \eta^N_{s})
        \int f^2(y)r(y, \eta^N_{s}) q_\theta(x,dy) 
    , \eta^N_{s}(dx) \rangle \\
& \qquad \qquad {}
    + \langle \mu(x, \eta^N_{s}) f^2(x) 
    , \eta^N_{s}(dx)\rangle
    \bigg\}ds. 
\end{aligned}    
\end{equation}
\end{definition}

@@

We write $\Pgen^N$
for the generator of the scaled population process $\eta^N$
of Definition~\ref{defn:mgale_construction}
acting on test functions of the form $F( \langle f, \eta \rangle )$,
where $f \geq 0$ is smooth and compactly supported on $\IR^d$ and 
$F \in C^\infty ([0,\infty))$.
Recall that $\theta \to \infty$ along with $N$,
although we don't remind the reader with extra superscripts.

A Taylor expansion allows us to write
\begin{multline*}
    \Pgen^N
    F(\langle f,\eta \rangle)
    =
    F'(\langle f, \eta \rangle)
    \lim_{\delta t\downarrow 0} \frac{1}{\delta t}
    \IE\left[
        \left. \langle f, \eta_{\delta t} \rangle
        -
        \langle f, \eta \rangle
        \right| \eta_0=\eta
    \right]
    \\
    \qquad {}
    + \frac{1}{2}
        F''(\langle f,\eta\rangle)
    \lim_{\delta t\downarrow 0}\frac{1}{\delta t}
    \IE\left[
        \left.\big(\langle f,\eta_{\delta t}\rangle
        -
        \langle f, \eta\rangle\big)^2 \right|\eta_0=\eta
    \right]
    +
    \epsilon_N(f, F, \eta),
\end{multline*}
where the terms that make up 
$\epsilon_N(f, F, \eta)$
will be negligible in our scaling limit.

@@

We now look at the second order term.
An individual at location $x$ gives birth 
to a surviving offspring at $y$ at rate
$$
\gamma(x,\eta) r(y,\eta) q_{\theta}(x, dy) ,
$$
and since this increments $\langle f, \eta \rangle$ by $f(y) / N$,
the contribution to the quadratic variation from birth events,
which occur at rate $\theta$ per individual 
(so, rate $N\theta |\eta|$ overall), is
$$
\langle
    N \theta \gamma(x,\eta)
    \int \frac{1}{N^2} f^2(y) r(y,\eta)
    q_\theta(x,dy) 
    , \eta(dx)
\rangle .
$$
Similarly, the increment in $\langle f, \eta\rangle$ resulting from 
the death of an individual at $x$ is $f(x)/N$, and so combining with the 
above, the second order term in the generator takes the form
\begin{align*}
& F''(\langle f,\eta\rangle)
\frac{1}{2} N \theta
\left\{
    \langle
        \gamma(x,\eta)
        \int \frac{1}{N^2}f^2(y)r(y,\eta)q_\theta(x,dy) 
    , \eta(dx)\rangle
    +
    \langle
        \mu(x,\eta)\frac{1}{N^2}f^2(x) 
    ,\eta(dx)\rangle
\right\} \\
&\qquad
= \frac{1}{2} F''(\langle f, \eta \rangle)
    \frac{\theta}{N}
    \langle
        \gamma(x, \eta) \int f^2(y) r(y, \eta) q_\theta(x, dy) + f^2(x) \mu(x, \eta),
        \eta(dx)
    \rangle .
\end{align*}
Since $\int f^2(y) r(y, \eta) q_\theta(x, dy) \to f^2(x) r(x, \eta)$
and $\gamma r + \mu = 2 \gamma r - F / \theta \to 2 \gamma r$
as $\theta \to \infty$,
this converges to
\begin{align*}
\frac{\alpha}{2} F''(\langle f, \eta \rangle)
    \langle
        2 \gamma(x, \eta) r(x, \eta),
        \eta(dx)
    \rangle .
\end{align*}

Finally, the term $\epsilon_{\theta,N}(f, F, \eta)$ will be 
$\bigO(\theta/N^2)$.

@@

% % % % % % % %
\begin{definition}[Martingale Problem Characterisation]
    \label{defn:lookdown_mgale}
For given positive values of $N$ and $\theta$
and $\lp_0 \in \mathcal{M}_F(\mathbb{R}^d \times [0,N])$,
we define $(\lp^{N}_t)_{t \geq 0}$
to be the unique solution to the martingale problem
with initial condition $\lp_0$ and generator $A^{N}$ that satisfies
\begin{equation*}
\begin{split}
& A^{N}f(\lp ) \\
&\quad =
    f(\lp)
    \,\sum_{(x,u)\in \lp}\,
    2 \gamma(x, \eta)
    \Bigg\{ \frac{1}{2N} \int_u^N g(x,u_1) du_1
            \frac{
                \theta \int_{\mathbb{R}^d}
                (g(y,u) - g(x,u))
                r(y, \eta) q_{\theta}(x,dy)
            }{ g(x,u) }
        \\
    &\qquad\qquad\qquad\qquad\qquad\qquad\qquad {} +
        \frac{\theta}{N} \int_u^N
        \int_{\mathbb{R}^d}\left(
            \frac{ g(y,u_1) + g(x,u_1) }{ 2 } - 1
        \right)
        r(y, \eta) q_{\theta}(x,dy)
        du_1
    \Bigg\}\\
    &\qquad\qquad {} +
    f(\lp) \sum_{(x,u)\in\lp}\,
    \left(
        \frac{\theta}{N} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q_\theta(x, dy) u^2 -b_{\theta}(x,\eta)u
    \right)
    \frac{\partial_u g(x,u)}{g(x,u)}
    ,
\end{split}
\end{equation*}
for all smooth functions $g \in C^{2}_{0}(\mathbb{R}^d)$,
where $f(\lp) = \prod_{(x, u) \in \lp} g(x, u)$ as defined in \eqref{eqn:test_functions},
and $\eta(\cdot) = \lp(\cdot \times [0, N]) / N$ is the scaled spatial pushforward of $\lp$,
as before.
\end{definition}

@@

In Appendix \ref{sec: Markov Mapping Theorem Application},
we will show that
if we define $\Gamma (d\textbf{u})$
as the probability kernel that corresponds to
assigning each particle an i.i.d. uniform $[0,N]$-level,
and for any $\lp \in \mathcal{M}_f(\mathbb{R}^d \times [0,\infty))$, we denote
$$\hat{f}(\lp)=\int f(\lp) \Gamma (d\textbf{u})$$ 
to be the spatial test functions with averaged level,
then the process
\begin{equation}
\begin{aligned}
M^{N}_t:=&\hat{f}(\lp_t)-\hat{f}(\lp_0)-\int_{0}^{t}\int   A^{N}f(\lp_s)\Gamma(d\textbf{u})ds\\
:=&\hat{f}(\lp_t)-\hat{f}(\lp_0)-\int_{0}^{t}   \Pgen^{N}\hat{f}(\lp_s)ds
\end{aligned}    
\end{equation}
is a martingale.

@@

Finally, we write $S(\tau_{[a]_k},t):=[\tau_{[a]_k},t]\times[0,\infty)\times\mathbb{R}^d \times \{0,1\}$.
Under this notation, for $t>\tau_{[a]_k}$,

@@

    Similarly, 
    \begin{align*}
        f(x, \smooth{r}\eta(y)) - f(x, \smooth{r}\eta(x))
        &=
        (\smooth{r}\eta(y) - \smooth{r}\eta(x)) f'(x, \smooth{r}\eta(x))
        + \frac{1}{2} (\smooth{r}\eta(y) - \smooth{r}\eta(x))^2 f''(x, m)
    \end{align*}
    for some $\smooth{r}\eta(x) \le m \le \smooth{r}\eta(y)$,
    where $f'$ and $f''$ denote the first and second derivatives with respect to the second argument.
    So,
    the second term in~\eqref{eqn:q_bound_split} is bounded by
    \begin{align*}
        \|f'\|_\infty
        \left|
            \theta \int_{\IR^d}
                (\smooth{r}\eta(y) - \smooth{r}\eta(x))
            q_\theta(x, dy)
        \right|
        +
        \|f''\|_\infty
        \left|
            \theta \int_{\IR^d}
                (\smooth{r}\eta(y) - \smooth{r}\eta(x))^2
            q_\theta(x, dy)
        \right| .
    \end{align*}
    Therefore, it suffices to show that there is a $K < \infty$ such that
    for all $\eta \in \measures$ and $x \in \IR^d$,
    \begin{equation}
        \label{eqn:first_moment_rho}
        \left|\theta \int_{\mathbb{R}^d}
            ( \smooth{r} \eta(y)-\smooth{r} \eta(x) )
        q_\theta(x,dy)\right|
        \leq K \smooth{\gamma} \eta(x)
    \end{equation}
    and
    \begin{equation}
        \label{eqn:second_moment_rho}
        \theta \int_{\mathbb{R}^d}
                \left( \smooth{r} \eta(y) - \smooth{r} \eta(x) \right)^2
        q_\theta(x,dy)
        \leq K \left(\smooth{\gamma}\eta(x) \right)^2 .
    \end{equation}
    Note that the right hand side of each is the average density
    over a wider region (since $\epsilon_\gamma > \epsilon_r$).

@@

        \theta \int_{\mathbb{R}^d}

@@

\begin{proof}
    Consider the semimartingale decomposition of Equation \eqref{eqn:eta_martingale},
    \begin{align} \label{eqn:eta_f_mgale_decomp}
        \langle f, \eta^N_t \rangle
        &=
        \langle f, \eta^N_0 \rangle
        + \int_0^t \int_{\IR^d} \left\{
            \gamma(x, \eta^N_s) B_f(x, \eta^N_s)
            + f(x) F(x, \eta^N_s)
            \right\} \eta^N_s(dx) ds
        + M^N_t(f) ,
    \end{align}
    where $M^N_t(f)$ is a martingale and for the moment we are defining
    \begin{equation*}
        B_f(x, \eta) = \int_{\IR^d} \theta (f(y) r(y, \eta) - f(x) r(x, \eta)) q_\theta(x, dy) .
    \end{equation*}
    By Lemma~\ref{lem:eta_compact_containment} and the assumption that $F$ is bounded above,
    $\gamma(x, \eta) B_f(x, \eta) + f(x) F(x, \eta) \le C_f$ for some $C_f$,
    and so, taking expectations,
    \begin{align*}
        \IE\left[ \langle f, \eta^N_t \rangle \right]
        &\le
        \IE\left[ \langle f, \eta^N_0 \rangle \right]
        + C_f \int_0^t \IE\left[ \langle f, \eta^N_s \rangle \right] dt .
    \end{align*}
    The bound then follows from Grownwall's inequality.
\end{proof}

@@

\begin{proof}
    First note that by Lemma~\ref{lem:eta_f_bound},
    $\IE[\langle 1, \eta^N_t \rangle] \le \IE[\langle 1, \eta^N_0 \rangle] e^{Ct}$
    for some $C$.
    Now, let $M^*_t(f) = \sup_{0 \le s \le t} M_t(f)$,
    and as before $[M(f)]_t$ the quadratic variation of $M_t(f)$,
    so that by the Burkholder-Davis-Gundy inequality, there is a $C'$ so that
    \begin{align*}
        \IE\left[ M^*_t(1) \right]
        &\le
        C' \IE\left[ \sqrt{[M^*(1)]_t} \right]
        \\ &\le
        C'\left( 1 + \IE\left[ [M^*(1)]_t \right] \right)
        \\ &=
        C'\left( 1 + \frac{\theta}{N} \IE\left[
            \int_0^t
            \int_{\IR^d} \left\{
                \gamma(x, \eta^N_s)
                \int_{\IR^d} r(y, \eta^N_s) q_\theta(x, dy)
                + \mu(x, \eta^N_s)
            \right\} \eta_s^N(dx)
            dt
            \right] \right)
        \\ &=
        C'\left( 1 + \IE\left[
            \int_0^t
            \int_{\IR^d} \left\{
                \frac{2\theta}{N} \gamma(x, \eta^N_s) r(x, \eta^N_s)
                + \frac{1}{N} B(x, \eta^N_s)
            \right\} \eta_s^N(dx)
            dt
            \right] \right) .
    \end{align*}
    Since $\gamma(x, \eta) r(x, \eta)$ and $B(x, \eta)$ are bounded,
    and $\theta/N \to \alpha < \infty$,
    combining constants and again using Gronwall's inequality, we get that
    \begin{align*}
        \IE\left[ M^*_t(1) \right]
        % &\le
        % C'\left( 1 + \IE\left[
        %     \int_0^t
        %     \int_{\IR^d} \left\{ C'' \right\} \eta_s^N(dx)
        %     dt
        %     \right] \right) \\
        &\le
        C' + C'' \IE[ \langle 1, \eta_0^N \rangle ] e^{tC} .
    \end{align*}
    Taking suprema and expectations on both sides of equation~\eqref{eqn:eta_f_mgale_decomp},
    then again using the fact that $\gamma(x, \eta) B(x, \eta) + F(x, \eta) \le C$,
    \begin{align*}
        \IE\left[\sup_{0 \le s \le t} \langle 1, \eta^N_s \rangle \right]
        &\le
        \IE[\langle 1, \eta^N_0 \rangle]
        + \IE\left[
            \sup_{0 \le s \le t}
            \int_0^t \int_{\IR^d} \left\{
                \gamma(x, \eta^N_s)
                B(x, \eta^N_s)
                + F(x, \eta^N_s)
            \right\} \eta^N_s(dx) ds
        \right]
        + \IE[M^*_t(1)] 
        \\
        &\le
        \IE[\langle 1, \eta^N_0 \rangle]
        + C \IE\left[
            \int_0^t \sup_{0 \le s \le t} \langle 1, \eta^N_s \rangle ds
        \right]
        + C' + C'' \IE[ \langle 1, \eta_0^N \rangle ] e^{tC} .
    \end{align*}
    Once again applying Gronwall's inequality,
    \begin{align*}
        \IE\left[\sup_{0 \le s \le t} \langle 1, \eta^N_s \rangle \right]
        &\le
        C'' 
        \left(\IE[\langle 1, \eta^N_0 \rangle] + C'\right)
        \IE[ \langle 1, \eta_0^N \rangle ] e^{2tC} .
    \end{align*}
    For any $T$,
    the inequality on the right is bounded above by a constant $C(T)$ independent of $N$.
    As a result, for any $K > 0$,
    \begin{equation*}
    \limsup_{N \to \infty}
        \IP\left[ \sup_{0 \le s \le T} \langle 1, \eta^{N}_{s} \rangle \geq K \right]
        \leq
        \frac{C(T)}{K}.
    \end{equation*}
\end{proof}

@@

\begin{lemma}[Tightness of $(\langle f, \eta^{N}_t \rangle )_{t>0}$]
    \label{lem:eta_projections_tightness}
For all $f \in C^{2}_{0}(\mathbb{R}^d)$, 
the collection of processes
$(\langle f, \eta^{N}_t \rangle)_{t \geq 0}$
for $N = 1, 2, \ldots$ is tight as a sequence of c\`adl\`ag, real-valued processes.
\end{lemma}

@@

\comment{
    Convergence of generators along (something like) the diagonal,
    taking $\epsilon \to 0$ at the same time as the other coefficient.
    (We won't prove tightness here.)
    This is where OneStepConvergence goes in.
}

In this section we prove Theorem~\ref{them:nonlocal_pde_limits}.

\todo[inline]{BEGIN OneStepConvergence}
These notes are an attempt of writing the one-step convergence of the particle system to a PDE limit.

\textbf{In this whole document $\rho_\epsilon$ will be the density of a normal with mean $0$ and variance $\epsilon^2$, and $q_\theta$ the density of a normal with mean $0$ and variance $1/\theta$. That is, $\rho_\epsilon(x) = p_{\epsilon^2}(x)$ and $q_\theta = p_{1/\theta}(x)$.}

>>>>

The model we work with is a fairly general model
of individuals living in continuous space.
We start with a population of
$\bigO(N)$ individuals per unit area distributed in $\IR^d$.
For applications, $d=1$ or $d=2$, but our results apply more generally.
The population will be distributed over a bounded region,
so the total number of individuals will also be $\bigO(N)$.
The population changes in continuous time, and
we describe the state of the population at time $t$ with a counting measure $X(t)$,
which assigns one unit of mass to the location of each individual.

@@

\begin{definition}[Martingale Problem Characterisation]
    \label{defn:mgale_construction},
For each value of $N$ and $\theta = \theta(N)$,
we define $(\eta^N_t)_{t \geq 0}$ to be the solution to the Martingale Problem,
with initial condition $\eta^N_0 \in \measures$,
such that for all smooth functions $f \in C^{\infty}_{0}(\IR^d)$,
writing $\langle f, \eta \rangle = \int_{\IR^d} f(x) \eta(dx)$
and $q_\theta(x, dy)$ as the Gaussian kernel
with mean $x + \meanq(x)/\theta$ and covariance $\covq(x) / \theta$,
\begin{equation}
    \label{eqn:eta_martingale}
\begin{aligned}
M^N_t(f)
&:=  \langle f, \eta^N_t \rangle
        -\langle f, \eta^N_0 \rangle
 \\ &\qquad {}
 -  \int_{0}^{t}\bigg\{
        \int\left( \int \theta
             \left(
                f(z)r(z, \eta^N_{s})
                - f(x)r(x, \eta^N_{s})
            \right)
        q_\theta(x,dz) \right)
\\ & \qquad \qquad \qquad \qquad {}
        \times \gamma(x, \eta^N_{s}) \eta^N_{s}(dx)
\\ & \qquad \qquad {}
    + \int f(x) F(x, \eta^N_{s}) \eta^N_{s}(dx)
    \bigg\} ds
\end{aligned}    
\end{equation}
is a martingale with quadratic variation
    \begin{equation} \label{eqn:prelimit_martingale_variation}
\begin{aligned} \relax
[ M^N_t(f)] =& 
\frac{\theta}{N} \int_{0}^{t}\bigg\{
    \langle \gamma(x, \eta^N_{s})
        \int f^2(y)r(y, \eta^N_{s}) q_\theta(x,dy) 
    , \eta^N_{s}(dx) \rangle \\
& \qquad \qquad {}
    + \langle \mu(x, \eta^N_{s}) f^2(x) 
    , \eta^N_{s}(dx)\rangle
    \bigg\}ds. 
\end{aligned}    
\end{equation}
\end{definition}

@@

We write $\Pgen^N$
for the generator of the scaled population process $\eta^N$
of Definition~\ref{defn:mgale_construction}
acting on test functions of the form $G( \langle f, \eta \rangle )$,
where $f \geq 0$ is smooth and compactly supported on $\IR^d$ and 
$G \in C^\infty ([0,\infty))$.
Recall that $\theta \to \infty$ along with $N$,
although we don't remind the reader with extra superscripts.

A Taylor expansion allows us to write
\begin{multline*}
    \Pgen^N
    G(\langle f,\eta \rangle)
    =
    G'(\langle f, \eta \rangle)
    \lim_{\delta t\downarrow 0} \frac{1}{\delta t}
    \IE\left[
        \left. \langle f, \eta_{\delta t} \rangle
        -
        \langle f, \eta \rangle
        \right| \eta_0=\eta
    \right]
    \\
    \qquad {}
    + \frac{1}{2}
        G''(\langle f,\eta\rangle)
    \lim_{\delta t\downarrow 0}\frac{1}{\delta t}
    \IE\left[
        \left.\big(\langle f,\eta_{\delta t}\rangle
        -
        \langle f, \eta\rangle\big)^2 \right|\eta_0=\eta
    \right]
    +
    \epsilon_N(f, G, \eta),
\end{multline*}
where the terms that make up 
$\epsilon_N(f, G, \eta)$
will be negligible in our scaling limit.

@@

We now look at the second order term.
An individual at location $x$ gives birth 
to a surviving offspring at $y$ at rate
$$
\gamma(x,\eta) r(y,\eta) q_{\theta}(x, dy) ,
$$
and since this increments $\langle f, \eta \rangle$ by $f(y) / N$,
the contribution to the quadratic variation from birth events,
which occur at rate $\theta$ per individual 
(so, rate $N\theta |\eta|$ overall), is
$$
\langle
    N \theta \gamma(x,\eta)
    \int \frac{1}{N^2} f^2(y) r(y,\eta)
    q_\theta(x,dy) 
    , \eta(dx)
\rangle .
$$
Similarly, the increment in $\langle f, \eta\rangle$ resulting from 
the death of an individual at $x$ is $f(x)/N$, and so combining with the 
above, the second order term in the generator takes the form
\begin{align*}
& G''(\langle f,\eta\rangle)
\frac{1}{2} N \theta
\left\{
    \langle
        \gamma(x,\eta)
        \int \frac{1}{N^2}f^2(y)r(y,\eta)q_\theta(x,dy) 
    , \eta(dx)\rangle
    +
    \langle
        \mu(x,\eta)\frac{1}{N^2}f^2(x) 
    ,\eta(dx)\rangle
\right\} \\
&\qquad
= \frac{1}{2} G''(\langle f, \eta \rangle)
    \frac{\theta}{N}
    \langle
        \gamma(x, \eta) \int f^2(y) r(y, \eta) q_\theta(x, dy) + f^2(x) \mu(x, \eta),
        \eta(dx)
    \rangle .
\end{align*}
Since $\int f^2(y) r(y, \eta) q_\theta(x, dy) \to f^2(x) r(x, \eta)$
and $\gamma r + \mu = 2 \gamma r - F / \theta \to 2 \gamma r$
as $\theta \to \infty$,
this converges to
\begin{align*}
\frac{\alpha}{2} G''(\langle f, \eta \rangle)
    \langle
        2 \gamma(x, \eta) r(x, \eta),
        \eta(dx)
    \rangle .
\end{align*}

Finally, the term $\epsilon_{\theta,N}(f, G, \eta)$ will be 
$\bigO(\theta/N^2)$.

@@

% % % % % % % %
\begin{definition}[Martingale Problem Characterisation]
    \label{defn:lookdown_mgale}
For given positive values of $N$ and $\theta$
and $\lp_0 \in \mathcal{M}_F(\IR^d \times [0,N])$,
we define $(\lp^{N}_t)_{t \geq 0}$
to be the unique solution to the martingale problem
with initial condition $\lp_0$ and generator $A^{N}$ that satisfies
\begin{equation*}
\begin{split}
& A^{N}f(\lp ) \\
&\quad =
    f(\lp)
    \,\sum_{(x,u)\in \lp}\,
    2 \gamma(x, \eta)
    \Bigg\{ \frac{1}{2N} \int_u^N g(x,u_1) du_1
            \frac{
                \theta \int_{\IR^d}
                (g(y,u) - g(x,u))
                r(y, \eta) q_{\theta}(x,dy)
            }{ g(x,u) }
        \\
    &\qquad\qquad\qquad\qquad\qquad\qquad\qquad {} +
        \frac{\theta}{N} \int_u^N
        \int_{\IR^d}\left(
            \frac{ g(y,u_1) + g(x,u_1) }{ 2 } - 1
        \right)
        r(y, \eta) q_{\theta}(x,dy)
        du_1
    \Bigg\}\\
    &\qquad\qquad {} +
    f(\lp) \sum_{(x,u)\in\lp}\,
    \left(
        \frac{\theta}{N} \gamma(x,\eta) \int_{\IR^d} r(y, \eta) q_\theta(x, dy) u^2 -b_{\theta}(x,\eta)u
    \right)
    \frac{\partial_u g(x,u)}{g(x,u)}
    ,
\end{split}
\end{equation*}
for all smooth functions $g \in C^{2}_{0}(\IR^d)$,
where $f(\lp) = \prod_{(x, u) \in \lp} g(x, u)$ as defined in \eqref{eqn:test_functions},
and $\eta(\cdot) = \lp(\cdot \times [0, N]) / N$ is the scaled spatial pushforward of $\lp$,
as before.
\end{definition}

@@

In Appendix \ref{sec: Markov Mapping Theorem Application},
we will show that
if we define $\Gamma (d\textbf{u})$
as the probability kernel that corresponds to
assigning each particle an i.i.d. uniform $[0,N]$-level,
and for any $\lp \in \mathcal{M}_f(\IR^d \times [0,\infty))$, we denote
$$\hat{f}(\lp)=\int f(\lp) \Gamma (d\textbf{u})$$ 
to be the spatial test functions with averaged level,
then the process
\begin{equation}
\begin{aligned}
M^{N}_t:=&\hat{f}(\lp_t)-\hat{f}(\lp_0)-\int_{0}^{t}\int   A^{N}f(\lp_s)\Gamma(d\textbf{u})ds\\
:=&\hat{f}(\lp_t)-\hat{f}(\lp_0)-\int_{0}^{t}   \Pgen^{N}\hat{f}(\lp_s)ds
\end{aligned}    
\end{equation}
is a martingale.

@@

Finally, we write $S(\tau_{[a]_k},t):=[\tau_{[a]_k},t]\times[0,\infty)\times\IR^d \times \{0,1\}$.
Under this notation, for $t>\tau_{[a]_k}$,

@@

    Similarly, 
    \begin{align*}
        f(x, \smooth{r}\eta(y)) - f(x, \smooth{r}\eta(x))
        &=
        (\smooth{r}\eta(y) - \smooth{r}\eta(x)) f'(x, \smooth{r}\eta(x))
        + \frac{1}{2} (\smooth{r}\eta(y) - \smooth{r}\eta(x))^2 f''(x, m)
    \end{align*}
    for some $\smooth{r}\eta(x) \le m \le \smooth{r}\eta(y)$,
    where $f'$ and $f''$ denote the first and second derivatives with respect to the second argument.
    So,
    the second term in~\eqref{eqn:q_bound_split} is bounded by
    \begin{align*}
        \|f'\|_\infty
        \left|
            \theta \int_{\IR^d}
                (\smooth{r}\eta(y) - \smooth{r}\eta(x))
            q_\theta(x, dy)
        \right|
        +
        \|f''\|_\infty
        \left|
            \theta \int_{\IR^d}
                (\smooth{r}\eta(y) - \smooth{r}\eta(x))^2
            q_\theta(x, dy)
        \right| .
    \end{align*}
    Therefore, it suffices to show that there is a $K < \infty$ such that
    for all $\eta \in \measures$ and $x \in \IR^d$,
    \begin{equation}
        \label{eqn:first_moment_rho}
        \left|\theta \int_{\IR^d}
            ( \smooth{r} \eta(y)-\smooth{r} \eta(x) )
        q_\theta(x,dy)\right|
        \leq K \smooth{\gamma} \eta(x)
    \end{equation}
    and
    \begin{equation}
        \label{eqn:second_moment_rho}
        \theta \int_{\IR^d}
                \left( \smooth{r} \eta(y) - \smooth{r} \eta(x) \right)^2
        q_\theta(x,dy)
        \leq K \left(\smooth{\gamma}\eta(x) \right)^2 .
    \end{equation}
    Note that the right hand side of each is the average density
    over a wider region (since $\epsilon_\gamma > \epsilon_r$).

@@

@@

\begin{proof}
    Consider the semimartingale decomposition of Equation \eqref{eqn:eta_martingale},
    \begin{align} \label{eqn:eta_f_mgale_decomp}
        \langle f, \eta^N_t \rangle
        &=
        \langle f, \eta^N_0 \rangle
        + \int_0^t \int_{\IR^d} \left\{
            \gamma(x, \eta^N_s) B_f(x, \eta^N_s)
            + f(x) F(x, \eta^N_s)
            \right\} \eta^N_s(dx) ds
        + M^N_t(f) ,
    \end{align}
    where $M^N_t(f)$ is a martingale and for the moment we are defining
    \begin{equation*}
        B_f(x, \eta) = \int_{\IR^d} \theta (f(y) r(y, \eta) - f(x) r(x, \eta)) q_\theta(x, dy) .
    \end{equation*}
    By Lemma~\ref{lem:gamma_bound} and the assumption that $F$ is bounded above,
    $\gamma(x, \eta) B_f(x, \eta) + f(x) F(x, \eta) \le C_f$ for some $C_f$,
    and so, taking expectations,
    \begin{align*}
        \IE\left[ \langle f, \eta^N_t \rangle \right]
        &\le
        \IE\left[ \langle f, \eta^N_0 \rangle \right]
        + C_f \int_0^t \IE\left[ \langle f, \eta^N_s \rangle \right] dt .
    \end{align*}
    The bound then follows from Grownwall's inequality.
\end{proof}

@@

\begin{proof}
    First note that by Lemma~\ref{lem:eta_f_bound},
    $\IE[\langle 1, \eta^N_t \rangle] \le \IE[\langle 1, \eta^N_0 \rangle] e^{Ct}$
    for some $C$.
    Now, let $M^*_t(f) = \sup_{0 \le s \le t} M_t(f)$,
    and as before $[M(f)]_t$ the quadratic variation of $M_t(f)$,
    so that by the Burkholder-Davis-Gundy inequality, there is a $C'$ so that
    \begin{align*}
        \IE\left[ M^*_t(1) \right]
        &\le
        C' \IE\left[ \sqrt{[M^*(1)]_t} \right]
        \\ &\le
        C'\left( 1 + \IE\left[ [M^*(1)]_t \right] \right)
        \\ &=
        C'\left( 1 + \frac{\theta}{N} \IE\left[
            \int_0^t
            \int_{\IR^d} \left\{
                \gamma(x, \eta^N_s)
                \int_{\IR^d} r(y, \eta^N_s) q_\theta(x, dy)
                + \mu(x, \eta^N_s)
            \right\} \eta_s^N(dx)
            dt
            \right] \right)
        \\ &=
        C'\left( 1 + \IE\left[
            \int_0^t
            \int_{\IR^d} \left\{
                \frac{2\theta}{N} \gamma(x, \eta^N_s) r(x, \eta^N_s)
                + \frac{1}{N} B(x, \eta^N_s)
            \right\} \eta_s^N(dx)
            dt
            \right] \right) .
    \end{align*}
    Since $\gamma(x, \eta) r(x, \eta)$ and $B(x, \eta)$ are bounded,
    and $\theta/N \to \alpha < \infty$,
    combining constants and again using Gronwall's inequality, we get that
    \begin{align*}
        \IE\left[ M^*_t(1) \right]
        % &\le
        % C'\left( 1 + \IE\left[
        %     \int_0^t
        %     \int_{\IR^d} \left\{ C'' \right\} \eta_s^N(dx)
        %     dt
        %     \right] \right) \\
        &\le
        C' + C'' \IE[ \langle 1, \eta_0^N \rangle ] e^{tC} .
    \end{align*}
    Taking suprema and expectations on both sides of equation~\eqref{eqn:eta_f_mgale_decomp},
    then again using the fact that $\gamma(x, \eta) B_f(x, \eta) + F(x, \eta) \le C$,
    \begin{align*}
        \IE\left[\sup_{0 \le s \le t} \langle 1, \eta^N_s \rangle \right]
        &\le
        \IE[\langle 1, \eta^N_0 \rangle]
        + \IE\left[
            \sup_{0 \le s \le t}
            \int_0^t \int_{\IR^d} \left\{
                \gamma(x, \eta^N_s)
                B_f(x, \eta^N_s)
                + F(x, \eta^N_s)
            \right\} \eta^N_s(dx) ds
        \right]
        + \IE[M^*_t(1)] 
        \\
        &\le
        \IE[\langle 1, \eta^N_0 \rangle]
        + C \IE\left[
            \int_0^t \sup_{0 \le s \le t} \langle 1, \eta^N_s \rangle ds
        \right]
        + C' + C'' \IE[ \langle 1, \eta_0^N \rangle ] e^{tC} .
    \end{align*}
    Once again applying Gronwall's inequality,
    \begin{align*}
        \IE\left[\sup_{0 \le s \le t} \langle 1, \eta^N_s \rangle \right]
        &\le
        C'' 
        \left(\IE[\langle 1, \eta^N_0 \rangle] + C'\right)
        \IE[ \langle 1, \eta_0^N \rangle ] e^{2tC} .
    \end{align*}
    For any $T$,
    the inequality on the right is bounded above by a constant $C(T)$ independent of $N$.
    As a result, for any $K > 0$,
    \begin{equation*}
    \limsup_{N \to \infty}
        \IP\left[ \sup_{0 \le s \le T} \langle 1, \eta^{N}_{s} \rangle \geq K \right]
        \leq
        \frac{C(T)}{K}.
    \end{equation*}
\end{proof}

@@

\begin{lemma}[Tightness of $(\langle f, \eta^{N}_t \rangle )_{t>0}$]
    \label{lem:eta_projections_tightness}
For all $f \in C^{2}_{0}(\IR^d)$, 
the collection of processes
$(\langle f, \eta^{N}_t \rangle)_{t \geq 0}$
for $N = 1, 2, \ldots$ is tight as a sequence of c\`adl\`ag, real-valued processes.
\end{lemma}

@@

In this section we prove Theorem~\ref{them:nonlocal_pde_limits},
which takes interaction distances to zero in the limit as well.

\todo[inline]{BEGIN OneStepConvergence}
\textbf{PREVIOUSLY, In this whole document $\rho_\epsilon$ will be the density of a normal with mean $0$ and variance $\epsilon^2$, and $q_\theta$ the density of a normal with mean $0$ and variance $1/\theta$. That is, $\rho_\epsilon(x) = p_{\epsilon^2}(x)$ and $q_\theta = p_{1/\theta}(x)$. This is HOPEFULLY FIXED NOW.}

\begin{theorem} \label{TeoremOneStepConvergence}
    Let $(\eta_t)_{t \geq 0}$ be the scaled particle system with $r(x, \eta) \equiv \gamma(x, \eta) \equiv 1$.
    Suppose $F(x)$ satisfies:
    \begin{enumerate}
        \item $F(x)1_{x>0}$  is bounded above.
        \item $|F'(x)1_{x>0}|$ is bounded,
        \item and $||F''(x)||_\infty < \infty$.
    \end{enumerate}
    We will also suppose $\theta$ is big enough that $1- F(x)1_{x>0}/\theta$ is non-negative.
